HBCC - sgACC - FEATURECOUNTS - GRCh38 - CQN

### 2020-05-19 individual-cohorts/HBCC_sgACC_FEATURECOUNTS_GRCh38_CQN.Rmd
test HBCC sgACC cohort

knit2synapse::createAndKnitToFolderEntity(file = "HBCC_sgACC_FEATURECOUNTS_GRCh38_CQN.Rmd",
                                          parentId ="syn21435176",
                                          folderName = 'HBCC - sgACC - DREAM - FEATURECOUNTS - GRCh38 - CQN')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn21435176';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of GRCh38 feature counts with CQN normalisation (sgACC)';

@@

COVARIATES <- droplevels(COVARIATES)
# Stepwise regression
phase1 <- mvBIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = base_formula,
                         data = bar,
                         variables = array(c("(1|Reported_Gender)", "scale(PMI)",
                                             "scale(ageOfDeath)", "scale(RIN)", "scale(RIN2)", "scale(EV.1)",
                                             "scale(EV.2)", "scale(EV.3)", "scale(EV.4)", "scale(EV.5)")))
phase1
```

#### Phase II (batch effects)
```{r phase2}
# Fit a base model with the following covariates
phase2 <- mvBIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = phase1$formula, 
                         data = COVARIATES,
                         variables = array(c("(1|LibraryBatch)", "(1|IsolationBatch)")))
phase2
```

#### Phase III (RNASeq alignment specific covariates)
```{r phase3}
# Fit a base model with the following covariates
phase3 <- mvBIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = phase2$formula, 
                         data = COVARIATES,
                         variables = array(c("scale(IntragenicRate)", "scale(IntronicRate)","scale(IntergenicRate)","scale(rRNARate)", 
                                             "scale(TotalReads)", "scale(GenesDetected)", "scale(MappedReads)")))
phase3
```

>>>>

knit2synapse::createAndKnitToFolderEntity(file = "HBCC_sgACC_FEATURECOUNTS_GRCh38_CQN.Rmd",
                                          parentId ="syn22012942",
                                          folderName = 'HBCC - sgACC - DREAM - FEATURECOUNTS - GRCh38 - CQN')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn22012942';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of GRCh38 feature counts with CQN normalisation (sgACC)';

@@

COVARIATES <- droplevels(COVARIATES)
# Stepwise regression
phase1 <- mvIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = base_formula,
                         data = bar,
                         variables = array(c("(1|Reported_Gender)", "scale(PMI)",
                                             "scale(ageOfDeath)", "scale(RIN)", "scale(RIN2)", "scale(EV.1)",
                                             "scale(EV.2)", "scale(EV.3)", "scale(EV.4)", "scale(EV.5)")))
phase1
```

#### Phase II (batch effects)
```{r phase2}
# Fit a base model with the following covariates
phase2 <- mvIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = phase1$formula, 
                         data = COVARIATES,
                         variables = array(c("(1|LibraryBatch)", "(1|IsolationBatch)")))
phase2
```

#### Phase III (RNASeq alignment specific covariates)
```{r phase3}
# Fit a base model with the following covariates
phase3 <- mvIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = phase2$formula, 
                         data = COVARIATES,
                         variables = array(c("scale(IntragenicRate)", "scale(IntronicRate)","scale(IntergenicRate)","scale(rRNARate)", 
                                             "scale(TotalReads)", "scale(GenesDetected)", "scale(MappedReads)")))
phase3
```
